Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-05-03 Manuscript Analyses/manuscript_analysis.Rmd
evaluated main effect of inhibitory control on int intel

effect_plot(mods2, list_sort_c, best_win) # Working Memory * Words in Noise Threshold
effect_plot(mods2, best_win, int = F) # Words in Noise Threshold
effect_plot(mods2, vocab_c, list_sort_c) # Receptive Vocabulary * Working Memory
effect_plot(mods2, card_sort_c, pattern_c) # Cognitive Flexibility * Processing Speed
effect_plot(mods2, pattern_c, card_sort_c) # Processing Speed * Cognitive Flexibility
effect_plot(mods2, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
effect_plot(mods2, best_win, flanker_c) # Words in Noise Threshold * Inhibitory Control
effect_plot(mods2, vocab_c, pattern_c, num = 4) # Receptive Vocabulary * Processing Speed
effect_plot(mods2, pattern_c, vocab_c, num = 4) # Processing Speed * Receptive Vocabulary
effect_plot(mods2, list_sort_c, card_sort_c) # Working Memory * Cognitive Flexibility
effect_plot(mods2, card_sort_c, list_sort_c) # Cognitive Flexibility * Working Memory

>>>>

effect_plot(mods2, list_sort_c, best_win) # Working Memory * Words in Noise Threshold
effect_plot(mods2, best_win, int = F) # Words in Noise Threshold
effect_plot(mods2, vocab_c, list_sort_c) # Receptive Vocabulary * Working Memory
effect_plot(mods2, card_sort_c, pattern_c) # Cognitive Flexibility * Processing Speed
effect_plot(mods2, pattern_c, card_sort_c) # Processing Speed * Cognitive Flexibility
effect_plot(mods2, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
effect_plot(mods2, best_win, flanker_c) # Words in Noise Threshold * Inhibitory Control
effect_plot(mods2, vocab_c, pattern_c, num = 4) # Receptive Vocabulary * Processing Speed
effect_plot(mods2, pattern_c, vocab_c, num = 4) # Processing Speed * Receptive Vocabulary
effect_plot(mods2, list_sort_c, card_sort_c) # Working Memory * Cognitive Flexibility
effect_plot(mods2, card_sort_c, list_sort_c) # Cognitive Flexibility * Working Memory
effect_plot(mods2, flanker_c, int = F) # Inhibitory Control
